
\documentclass{article}
\usepackage{amsmath}
\usepackage{geometry}
\geometry{margin=1in}
\begin{document}

\section*{Problem 10: Validity of Euler’s Equations Near a Wall}

\subsection*{Question}
In the context of fluid flow over a flat plate, why is Euler’s equation not valid near the wall?

\begin{itemize}
  \item[(a)] The pressure gradient is zero near the wall
  \item[(b)] The flow near the wall has high Reynolds number
  \item[(c)] Viscous effects dominate in the flow near the wall
  \item[(d)] The statement is false. Euler equation is valid near the wall
\end{itemize}

\subsection*{Euler’s Equations}
Euler’s equations for an inviscid flow:
\[
\rho \left( \frac{\partial \vec{v}}{\partial t} + \vec{v} \cdot \nabla \vec{v} \right) = -\nabla p + \rho \vec{g}
\]

They neglect viscous effects and cannot capture no-slip boundary conditions or velocity gradients near walls.

\subsection*{Flow Over a Flat Plate}
\begin{itemize}
  \item A boundary layer forms at the wall.
  \item Inside the boundary layer, viscous effects dominate.
  \item Hence, Euler’s equations are not valid within the boundary layer.
\end{itemize}

\subsection*{Option Analysis}
\begin{itemize}
  \item[(a)] Incorrect – Pressure gradient can exist near the wall.
  \item[(b)] Incorrect – High Re does not mean inviscid behavior near the wall.
  \item[(c)] \textbf{Correct} – Viscosity dominates near the wall.
  \item[(d)] Incorrect – Euler’s equations do not apply near the wall.
\end{itemize}

\subsection*{Answer}
\[
\boxed{\text{(c) Viscous effects dominate in the flow near the wall}}
\]

\end{document}
